---
title: "Final Project EPI 190R"
author: "Olivia Christman"
format: html
execute:
  echo: false
---


```{r}
#| echo: false
#| output: false 
library(tidyverse)
library(gtsummary)
library(readr)
library(here)

ikea <-read_csv (here::here("data","ikea.csv")) %>%
  select (-...1) |>
  na.omit (ikea) |>
mutate(sellable_online_cat = factor(sellable_online, labels = c ("Yes", "No")),
       other_colors_cat = factor (other_colors, labels = c("Yes","No")),
       category2 = factor (category, labels = c("Bar furniture","Beds",
                    "Bookcases & shelving units","Cabinets & cupboards",
                      "Cafe furniture", "Chairs", "Chests of drawers & drawer units", "Children's furniture", "Nursery furniture", "Outdoor Furniture", "Room dividers","Sideboards, buffets & console tables", "Sofas & armchairs", "Tables & desks","Trolleys", "TV & media furniture", "Wardrobes"))) 
  
```

This Dataset describes Ikea Furniture and was found on Kaggle and was created using Ikeas website. @tbl-one describes the categories of furniture, price, and availability.

```{r}
#| label: tbl-one
#| tbl-cap: "Descriptive Statistics"
table1 <-tbl_summary(
      ikea,
      include = c(category2, price, sellable_online_cat, other_colors_cat),
      label = list(
       category2 ~ "Furniture type",
       price ~ "Price",
      sellable_online_cat ~ "Available for sale online",
      other_colors_cat ~ "Available in another color"
      ),
  missing_text = "Missing"
  )
table1
```

```{r}
#| output: false
inline_text(table1, variable =  "price", column = "stat_0")

stats <- list(n=nrow(ikea),
              mean_height = mean(ikea$height))
```

Their is a total of `r stats$n` pieces of furniture included in this dataset with median and (Q1, Q3) price of (`r inline_text ( table1, variable =  "price", column = "stat_0")`). The average height of a piece of ikea furniture is `r stats$mean_height`. @tbl-two below is univariate regression of how furniture type, availability online, and availability of color is associated with price. 

```{r}
#| label: tbl-two
#| tbl-cap: Linear Regression of Price 
regression <- tbl_uvregression(
         ikea,
         y = price,
         include = c(category2, sellable_online_cat, other_colors_cat),
         method = lm
)
regression
```

@fig-hist shows a graph of Ikea furniture prices
``` {r}
#| label: fig-hist
#| fig-cap: Historgram of Price of Furniture

p <- ggplot(ikea, aes(x=price)) + geom_histogram()

p
```

```{r}
#| output: false
#Save Histogram
ggsave(plot = p,
       filename= here::here("Documents","fig.pdf"))

```
